Type Refinements for the Working Class

### 2015-12-19 paper.tex
wording

Stated internally as a presheaf in the topos, the meaning of parametric typehood for
$\phi$ is perhaps a bit more clear:
\[
  \Define{
    \IsType{-}{\phi}{\tau}
  }{
    \prod_{L,M,N\in\Exprs_\tau}
    {\phi(L,N)}^{L\sim_\tau M \times \phi(M,N)}
  }
\]

@@

\begin{definition}[Value Types]
  We can give a simple characterization of Martin-L\"of's \emph{value types} in
  terms of our computation types. For any type $\IsType{\Upsilon}{\phi}{\tau}$,
  we will say $\IsValueType{\Upsilon}{\phi}{\tau}$ in case $\phi$ is equal to
  its closure, i.e.\ $\EqRefines{\Upsilon}{\phi}{\underline{\phi}}{\tau}$.
\end{definition}

>>>>

Stated internally as an object in the topos, the meaning of parametric typehood for
$\phi$ is perhaps a bit more clear:
\[
  \Define{
    \IsType{-}{\phi}{\tau}
  }{
    \prod_{L,M,N\in\Exprs_\tau}
    {\phi(L,N)}^{L\sim_\tau M \times \phi(M,N)}
  }
\]

@@

\begin{definition}[Value Types]
  We can give a simple characterization of Martin-L\"of's \emph{value types} in
  terms of our more general computational types. For any type $\IsType{\Upsilon}{\phi}{\tau}$,
  we will say $\IsValueType{\Upsilon}{\phi}{\tau}$ in case $\phi$ is equal to
  its closure, i.e.\ $\EqRefines{\Upsilon}{\phi}{\underline{\phi}}{\tau}$.
\end{definition}
